A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-26 article/02_Materials_and_Methods.Rmd
language in materials&methods

The distribution of the $k$ variants within the groups can be observed for every time step and documented in time series just like the ones for the real-world regions data (Figure \ref{development_burial_type} B and \ref{development_burial_construction} B). These time series can as well be used to calculate time series of region-region distance, which again can be split up into time blocks of 200 years to calculate mean distance matrices. The latter can be checked for correlation with the spatial distance matrix (cf. Table \ref{tab:distanceandcorrelationtable*} AB) and compared with other simulation results and real-world observations (Figure \ref{simulation}).

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/simulation.jpeg}
\caption{\label{simulation}Development of correlation between cultural and spatial distance for real world data and simulation results. The plots in the left column of the plot matrix (\textbf{ACE}) contain simulation results for an equal group distance matrix $I$, the ones on the right (\textbf{BDF}) for a distance matrix based on the macro unit distances defined for this paper (Figure \ref{map_regions} B). The rows of the plot matrix (\textbf{AB}, \textbf{CD}, \textbf{EF}) represent different degrees of intergroup transmission $m_i$. Each plot shows the results of 50 simulation runs. The x-axis displays the time distinguished into 200 year time slots, the y-axis Spearman's rank correlation coefficient between the mean squared Euclidean distance matrix for a 200 year time slot and the static spatial distance matrix. This information is visualized for each time slot with (from left to right) a dotplot coloured according to the $p$-value of the Mantel test, a scatter plot line and a boxplot. The scatter plot points of one simulation run are connected with a faint line from one time slot to the next. To compare the runs with the real world observations, the results for the burial customs data (Table \ref{tab:distanceandcorrelationtable*} AB) is added here with with a stronger solid (\textit{burial type}) and dashed (\textit{burial construction}) line. The strong horizontal line marks the correlation coefficient of zero, where neither positive nor negative correlation can be assumed.}
\end{figure*}

>>>>

The distribution of the $k$ variants within the groups can be observed for every time step and documented in time series like the ones for the real-world regions data (Figure \ref{development_burial_type} B and \ref{development_burial_construction} B). These time series can as well be used to calculate time series of region-region distance, which again can be split up into time blocks of 200 years to calculate mean distance matrices. The latter can be checked for correlation with the spatial distance matrix (cf. Table \ref{tab:distanceandcorrelationtable*} AB) and compared with other simulation results and real-world observations (Figure \ref{simulation}).

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../analysis/figures/simulation.jpeg}
\caption{\label{simulation}Development of correlation between cultural and spatial distance for real world data and simulation results. The plots in the left column of the plot matrix (\textbf{ACE}) contain simulation results for an equal group distance matrix $I$, the ones on the right (\textbf{BDF}) for a distance matrix based on the macro unit distances defined for this paper (Figure \ref{map_regions} B). The rows of the plot matrix (\textbf{AB}, \textbf{CD}, \textbf{EF}) represent different degrees of intergroup transmission $m_i$. Each plot shows the results of 50 simulation runs. The x-axis displays the time distinguished into 200 year time slots, the y-axis Spearman's rank correlation coefficient between the mean squared Euclidean distance matrix for a 200 year time slot and the static spatial distance matrix. This information is visualized for each time slot with (from left to right) a dotplot coloured according to the $p$-value of the Mantel test, a scatter plot line and a boxplot. The scatter plot points of one simulation run are connected with a faint line from one time slot to the next. To compare the runs with the real world observations, the results for the burial customs data (Table \ref{tab:distanceandcorrelationtable*} AB) is added here with a stronger solid (\textit{burial type}) and dashed (\textit{burial construction}) line. The strong horizontal line marks the correlation coefficient of zero, where neither positive nor negative correlation can be assumed.}
\end{figure*}
